Generative Adversarial Networks

### 2017-12-04 cs6735/project/report.tex
small updates (computer is crashing)

These architectures are better suited for multi-modal output (see section \ref{sec:img2img}) as they are able to provide better data representations \citep{2017arXiv171007035C}. By conditioning the GAN, it is possible to control the data generation process. This additional input may be class label or other items such as text or an image. For example, given that a CGAN was conditioned on sentences, one may be able to describe a scenario and have that scenario synthesized as an image \citep{2016arXiv160505396R}. In section \ref{sec:img2img}, we will see how conditional GANs are applied to image translation tasks.

\subsection{Inference GANs} \label{sec:inferencegan}
The first GAN architectures lacked the ability to map an sample $x$ to its associated latent vector $z$. The ability to do this is often referred to as having an \textit{inference mechanism} \citep{2017arXiv171007035C}. In 2016, two new architectures were independently proposed which introduced this mechanism by adding an inference network \citep{2016arXiv160509782D, 2016arXiv160600704D}. This new architecture involves two generative models, a decoder and encoder, which work together to fool the discriminator. The discriminator is now trained with a sample $x$ and latent space vector $z$ and has to decide if the pair is a real sample and its encoding or generated image and its associated latent space input. This architecture allows the encode to learn the mapping of $x$ to $z$. Furthermore, it generates a set of continuous variables. That is, if the vector $z$ is of length $n$, then $n$ means and $n$ variances will be generated. This allows for a probability distribution for each value of $z$. However, the reconstructed images still remain of poor quality \citep{2017arXiv171007035C}.

\subsection{Progressive GANs} \label{sec:proggans}
Progressive GANs do not offer an architecture variation but a new training methodology for training GANs. Introduced in October 2017 by Karras \textit{et al.} \citep{2017arXiv171010196K}, these networks incrementally increase the number of convolutions within both the generator and discriminator. Each new convolution is only added after the previous GAN converges. This permits the generator to progressively discover the image distribution, increases the training speed and reduces training instability \citep{2017arXiv171010196K}. Combined with new normalization techniques, progressive GANs allow for much higher resolution images to be generated \citep{2017arXiv171010196K}. The experimental results offer promising new directions for GAN research and applications.

\begin{figure}
\centering
\includegraphics[scale=0.45]{progressive_growing}
\caption{The training process of progressively growing generative adversarial networks recently introduced by Karras \textit{et al.} \citep{2017arXiv171010196K}. The generator and discriminator begin at $4x4$ resolution and progressively grow generate and discriminate $1024x1024$ resolution images.}
\label{fig:ProgressiveGrowingGAN}
\end{figure}

\section{Latent Space} \label{sed:latentspace}
The generator model of a GAN must internalize a representation of the data that it is trained on. This quality is shared with variatinal autoencoders and word linguistic models such as \textit{word2vec} \citep{2017arXiv171007035C}. One interesting characteristic of the latent space is that it is typically of lower dimension than the training data \citep{2017arXiv171007035C}. This forces the model to efficiently represent the training data by extracting only useful features. As long as the effects of mode collapse are minimal, the latent space can be highly structured \citep{2017arXiv171007035C}. We often observe semantic transformations when interpolations are conducted. For example, movement of the latent vector in certain directions may alter rotation, produce colour changes or see the addition of attributes such as eyeglasses \citep{2017arXiv171007035C}.

@@

\begin{figure}
\centering
\includegraphics[scale=0.40]{smile_concept_vector}
\caption{The addition of the "smile" concept vector (far right) to a vector associated with a woman (far left). The images in-between were created through an interpolation of the two vectors. Example retrieved form Dumoulin \textit{et al.} \citep{2016arXiv160600704D}.}
\label{fig:conceptvector}
\end{figure}

\section{Applications} \label{sec:applications}
Although GANs are a relatively new invention, many different applications have already been discovered. Several of the reoccurring themes are elaborated within this section.

@@

\begin{figure}
\centering
\includegraphics[scale=0.9]{multimodal}
\caption{An example of scenario where the ability to model multi-modal data is incredibly important. This figure demonstrates the process of predicting the next video frame given the previous one. A generator trained with mean squared error (middle) produces an image which averages each possible future. When using an adversarial process (right), the image produced corresponds with the most likely scenario. Example retrieved form Lotter \textit{et al.} \citep{2015arXiv151106380L}.}
\label{fig:multimodal}
\end{figure}

\subsubsection{Image Super-Resolution}
Image super-resolution is the process of generating a high resolution image from a lower resolution image by inferring details. For each lower resolution sample, there exists multiple possible correct outputs. Due to this characteristic, GANs are optimally suited for this task. The Super-Resolution GAN (SRGAN) proposed by Ledig \textit{et al.} remains similiar to other GANs; however, the discriminator is trained to distinguish real images from super-resolution images \citep{2016arXiv160904802L}. SRGANs infer photo characteristics with respect to domain of training set \citep{2017arXiv171007035C}. Therefore, it is essential to train different models for each domain of images.

\subsubsection{Image-to-Image Translation}
Image-to-image translation has made astounding progress and offers many yet undiscovered applications \citep{2017arXiv170100160G}. This process includes the translation of images from a source domain $X$ to the target domain $Y$. The translated images are then compared against images from the target domain and the generator parameters are updated as to reduce the distance between the translated and real images. An example of this operation can be visualized in figure \ref{fig:img2img}. Conditional networks are well suited for this task and there exists several different GAN architectures which take advantage of their characteristics to preform these translations \citep{2016arXiv161107004I, 2017arXiv171111585W, 2017arXiv170310593Z}. Recent work by Zhu \textit{et al.} demonstrate the feasibility of unpaired image-to-image translation by introducing a cycle consistency loss to enforce $F(G(X)) \approx X$ where $G$ is the mapper and $F$ is the inverse mapper \citep{2017arXiv170310593Z}. Furthermore, research released in November 2017 by Wang \textit{et al.} further improve the general quality of synthesized images \citep{2017arXiv171111585W}. Their semantic map translations are now almost indistinguishable from real images.

\begin{figure}
\centering
\includegraphics[scale=0.55]{img2img}
\caption{Examples of the image-to-image technique developed by Isola \textit{et al.} \citep{2016arXiv161107004I}. This technique makes use of conditional generative adversarial networks to map across image domains.}
\label{fig:img2img}
\end{figure}

\subsection{Semi-Supervised Learning} \label{sec:semisupervised}
There exist several techniques for training a classifier using a GAN. These methods all take advantage of the unsupervised aspect of GANs to implement semi-supervised learning. The ability to use GAN for unsupervised learning also offers a quantitative method to rank different GAN models.

One method involves the use of transfer learning. After the GAN training process has completed, the discriminator may be used within classification tasks as a feature extractor. A new machine learning model, such as a support vector machine (SVM), is trained on the extracted features of some layer $l$ of the discriminator. Another transfer learning approach makes use of the inference GANs mentioned in section \ref{sec:inferencegan}. Similar to the previous technique, a new machine learning model is trained on the last three hidden layers of the of the encoder. These methods have both received state-of-the-art classification results \citep{2017arXiv171007035C}.

Another general approach to semi-supervised learning involves the transformation of the discriminator into a classifier. Given that there are $k$ different labels, the new classifier will have $k + 1$ classes where the $k + 1$ class is associated with a fake image. When a real image is given to the discriminator, it attempts to classify the sample as one of the $k$ classes; however, when a generated or unlabeled image is given, the probabilities of the k classes are summed together to represent the probability of the image being real. In this situation, the classifier reverts back to its discriminative behavior. Typical supervised models need more than $50,000$ samples whereas state of the art performance can be achieved on labeled datasets ranging from $20$ to $8,000$ samples using this technique \citep{2017arXiv170100160G}.

@@

\section{Conclusion}
GANs are generative models which allow us to parametrize complicated probability distribution functions. They can be used to generate, modify and manipulate images. Furthermore, they allow for the use novel techniques within the context of reinforcement learning and unsupervised learning. Today, they are already being applied to many problems \citep{genmodelingopenai}; however, the majority of their applications have yet to be discovered. As long as the research effort continues, GANs promise exciting new avenues within the field of machine learning.

>>>>

These architectures are better suited for multi-modal output (see section \ref{sec:img2img}) as they are able to provide better data representations \citep{2017arXiv171007035C}. By conditioning the GAN, it is possible to control the data generation process. This additional input may be class label or other items such as text or an image. For example, given that a CGAN was conditioned on sentences, one may be able to describe a scenario and have that specific scenario synthesized as an image \citep{2016arXiv160505396R}. In section \ref{sec:img2img}, we will see how CGANs are applied to image translation tasks.

\subsection{Inference GANs} \label{sec:inferencegan}
The first GAN architectures lacked the ability to map an sample $x$ to its associated latent vector $z$. The ability to do this is often referred to as having an \textit{inference mechanism} \citep{2017arXiv171007035C}. In 2016, two new architectures were independently proposed which both introduced this mechanism by adding an inference network \citep{2016arXiv160509782D, 2016arXiv160600704D}. This new architecture involves two generative models, a decoder and encoder, which work together to fool the discriminator. Instead of only receiving a sample $x$, the discriminator is also trained on a latent space vector $z$ and has to decide if the pair is a real sample and its encoding or generated sample and its associated latent space vector. This architecture allows the encoder to learn the mapping of $x$ to $z$. Furthermore, the encoder generates a set of continuous variables. That is, if the vector $z$ is of length $n$, then $n$ means and $n$ variances will be generated. This allows for a probability distribution for each value of $z$. However, the reconstructed images still remain of poor quality \citep{2017arXiv171007035C}.

\subsection{Progressive GANs} \label{sec:proggans}
Progressive GANs do not offer an architecture variation but a new training methodology. Introduced in October 2017 by Karras \textit{et al.} \citep{2017arXiv171010196K}, these networks incrementally increase the number of convolutions within the generator and discriminator. A new convolution is added after the previous generator converges until a limit is reached. This permits the generator to progressively discover the image distribution. This technique also increases training speed and improves training stability \citep{2017arXiv171010196K}. Combined with new normalization techniques, progressive GANs allow for much higher resolution images to be generated \citep{2017arXiv171010196K}. The experimental results received by Karras offer promising new directions for GAN research and applications.

\begin{figure}
\centering
\includegraphics[scale=0.45]{progressive_growing}
\caption{The training process of progressively growing generative adversarial networks recently introduced by Karras \textit{et al.} \citep{2017arXiv171010196K}. The generator and discriminator begin at $4x4$ resolution and progressively grow to generate and discriminate $1024x1024$ resolution images.}
\label{fig:ProgressiveGrowingGAN}
\end{figure}

\section{Latent Space} \label{sed:latentspace}
The generator model of a GAN must internalize a representation of the data that it is trained on. This quality is shared with variatinal autoencoders and word linguistic models such as \textit{word2vec} \citep{2017arXiv171007035C}. One interesting characteristic of the latent space is that it is typically of lower dimension than the training data \citep{2017arXiv171007035C}. This forces the model to efficiently represent the training data by extracting only useful features. As long as the effects of mode collapse are minimal, the latent space is often highly structured \citep{2017arXiv171007035C}. We may observe semantic transformations when interpolations are conducted. For example, movement of the latent vector in certain directions may alter rotation, produce colour changes or see the addition of attributes such as eyeglasses \citep{2017arXiv171007035C}.

@@

\begin{figure}
\centering
\includegraphics[scale=0.40]{smile_concept_vector}
\caption{The addition of the "smile" concept vector (far right) to a vector associated with a woman (far left). The images in-between were created through an interpolation of the two vectors. Example retrieved from Dumoulin \textit{et al.} \citep{2016arXiv160600704D}.}
\label{fig:conceptvector}
\end{figure}

\section{Applications} \label{sec:applications}
Although GANs are a relatively new in the field of machine learning, many different applications have already been discovered. Several of the reoccurring themes are elaborated within this section.

@@

\begin{figure}
\centering
\includegraphics[scale=0.9]{multimodal}
\caption{An example of scenario where the ability to model multi-modal data is incredibly important. This figure demonstrates the process of predicting the next video frame given the previous one. A generator trained with mean squared error (middle) produces an image which averages each possible future. When using an adversarial process (right), the image produced corresponds with the most likely scenario and is not blurry unlike the image generated using MSE. Example retrieved form Lotter \textit{et al.} \citep{2015arXiv151106380L}.}
\label{fig:multimodal}
\end{figure}

\subsubsection{Image Super-Resolution}
Image super-resolution is the process of generating a high resolution image from a lower resolution image by inferring details. For each lower resolution sample, there exists multiple possible correct outputs. Due to this characteristic, GANs are optimally suited for this task. The Super-Resolution GAN (SRGAN) proposed by Ledig \textit{et al.} uses the conditional GAN architecture. The discriminator is trained to distinguish real images from super-resolution images \citep{2016arXiv160904802L}. SRGANs infer photo characteristics with respect to tje domain of training set \citep{2017arXiv171007035C}. Therefore, it is essential to train different models for each domain of images.

\subsubsection{Image-to-Image Translation}
Image-to-image translation has made astounding progress recently and offers many yet undiscovered applications \citep{2017arXiv170100160G}. This process includes the translation of images from a source domain $X$ to the target domain $Y$. The translated images are then compared against images from the target domain and the generator parameters are updated as to reduce the distance between the translated and real images. An example of this operation can be visualized in figure \ref{fig:img2img}. Conditional networks are well suited for this task and there exists several different GAN architectures which take advantage of their characteristics to preform these translations \citep{2016arXiv161107004I, 2017arXiv171111585W, 2017arXiv170310593Z}. Recent work by Zhu \textit{et al.} demonstrate the feasibility of unpaired image-to-image translation by introducing a cycle consistency loss to enforce $F(G(X)) \approx X$ where $G$ is the mapper and $F$ is the inverse mapper \citep{2017arXiv170310593Z}. Furthermore, research released in November 2017 by Wang \textit{et al.} further improve the general quality of synthesized images \citep{2017arXiv171111585W}. Their semantic map translations are now almost indistinguishable from real images.

\begin{figure}
\centering
\includegraphics[scale=0.55]{img2img}
\caption{Examples of the image-to-image technique developed by Isola \textit{et al.} \citep{2016arXiv161107004I}. This method makes use of conditional generative adversarial networks to map across image domains.}
\label{fig:img2img}
\end{figure}

\subsection{Semi-Supervised Learning} \label{sec:semisupervised}
There exist several techniques for training a classifier using a GAN. These methods all take advantage of the unsupervised aspect of GANs to implement semi-supervised learning. The ability to use GAN for semi-supervised learning also offers a quantitative method to rank different GAN models.

One method involves the use of transfer learning. After the GAN training process has completed, the discriminator may be used within classification tasks as a feature extractor. A new machine learning model, such as a support vector machine, is trained on the extracted features of some layer $l$ of the discriminator. Another transfer learning approach makes use of inference GANs. A new machine learning model is trained on the last three hidden layers of the of the encoder. These methods have both received state-of-the-art classification results \citep{2017arXiv171007035C}.

Another general approach to semi-supervised learning involves the transformation of the discriminator into a classifier. Given that there are $k$ different labels for some classification task, the new classifier will have $k + 1$ classes where the $k + 1$ class is associated with a fake sample. When a real sample is given to the discriminator, it attempts to classify the sample as one of the $k + 1$ classes; however, when a generated or unlabeled sample is given, the probabilities of the k classes are summed together to represent the probability of the sample being real. In this situation, the classifier reverts back to its discriminative behavior. Typical supervised models need more than $50,000$ samples whereas state-of-the-art performance can be achieved on labeled datasets ranging from $20$ to $8,000$ samples using this technique \citep{2017arXiv170100160G}.

@@

\section{Conclusion}
GANs are generative models which allow us to parametrize complicated probability distribution functions. They can be used to generate, modify and manipulate images. Furthermore, they allow for the use novel techniques within the context of reinforcement learning and semi-supervised learning. Today, they are already being applied to many problems \citep{genmodelingopenai}; however, the majority of their applications have yet to be discovered. As long as the research effort continues, GANs promise exciting new research avenues within the field of machine learning.
